Transparent Changes

### 2022-05-23 scripts/comparison.Rmd
Change legend in example plot

p_ex <- ggplot(exm_tidy, aes(x = time)) +
  geom_point(data = exm_tidy[exm_tidy$method == "raw", ], aes(y = value), alpha = 0.1) +
  geom_line(data = exm_tidy[exm_tidy$method %in% c("Moving Breath", "Moving Time", "Digital Filter"), ], aes(y = value, color = method), size = 0.7) +
  geom_point(data = exm_tidy[exm_tidy$method == "Binned Time", ], aes(y = value, fill = method, colour = "Binned Time"), size = 1.4) +
  scale_x_continuous(
    name = "Time (min)",
    limits = c(500,860),
    breaks = c(540, 630, 720),
    labels = c(8, 10, 12),
    expand = c(0,0)
  ) +
  scale_y_continuous(
    name = "VO2 (ml/min/kg)",
    limits = c(55,75)
  ) +
  scale_color_manual(
    name = "Processing Strategy",
    values = c(met.brewer("Java", 3)[3], "blue", met.brewer("Java", 3)[c(1,2)]),
    labels = c("Binned Time", "Digital Filter","Moving Time","Moving Breath"),
    guide = guide_legend(
      reverse = TRUE,
      override.aes = list(
        linetype = c(rep.int("solid", 3), "blank"),
        shape = c(rep.int(NA, 3), 19),
        color = c(met.brewer("Java", 3)[c(1,2)], "blue", met.brewer("Java", 3)[3])
      )
    )
  ) +
   scale_fill_manual(
    values = "white",
    guide = "none"
  ) +
  theme_classic() +
  theme(
    legend.position = c(0.88, 0.6),
  )

>>>>

p_ex <- ggplot(exm_tidy, aes(x = time)) +
  geom_point(
    data = exm_tidy[exm_tidy$method == "raw", ], 
    aes(y = value, alpha = method, colour = "Raw Data")
  ) +
  geom_line(
    data = exm_tidy[exm_tidy$method %in% c("Moving Breath", "Moving Time", "Digital Filter"), ], 
    aes(y = value, color = method), 
    size = 0.7
  ) +
  geom_point(
    data = exm_tidy[exm_tidy$method == "Binned Time", ], 
    aes(y = value, fill = method, colour = "Binned Time"), 
    size = 1.4
  ) +
  scale_x_continuous(
    name = "Time (min)",
    limits = c(500,860),
    breaks = c(540, 630, 720),
    labels = c(8, 10, 12),
    expand = c(0,0)
  ) +
  scale_y_continuous(
    name = "VO2 (ml/min/kg)",
    limits = c(55,75)
  ) +
  scale_color_manual(
    name = "Processing Strategy",
    values = c(met.brewer("Java", 3)[3], "blue", met.brewer("Java", 3)[c(1,2)], "black"),
    labels = c("Raw Data", "Binned Time", "Digital Filter","Moving Time","Moving Breath"),
    guide = guide_legend(
      reverse = TRUE,
      override.aes = list(
        linetype = c(rep.int("solid", 3), "blank", "blank"),
        shape = c(rep.int(NA, 3), 19, 19),
        color = c(met.brewer("Java", 3)[c(1,2)], "blue", met.brewer("Java", 3)[3], "black"),
        alpha = c(rep.int(1, 4), 0.1)
      )
    )
  ) +
  scale_fill_manual(
    values = "white",
    guide = "none"
  ) +  scale_alpha_manual(
    values = 0.1,
    guide = "none"
  ) +
  theme_classic() +
  theme(
    legend.position = c(0.88, 0.63),
  )
